Scikit-learn: machine learning without learning the machinery

### 2014-05-22 article.tex
Iter on paper

\paragraph{Model evaluation and parameter selection.}
%
The data used to train a model can be used to measure the prediction
error, as it would be enable to distinguish noise from signal, and thus
overly optimistic. The correct way is to leave out \emph{test} data,
untouched during training. Often a \emph{cross-validation} scheme is
used, where the data is repeatedly split into \emph{train} and
\emph{test} subsets. Scikit-learn provides a complete framework for
cross-validation. Specific iterators are used to describe the subsets and
several functions and objects accept as arguments these iterators to
perform cross-validation internally. For instance the {\tt
cross\_val\_score} function measures the prediction score of an
estimator. Cross-validation can also be used to tuned the meta-parameters
of an estimator, such as the sparsity of a sparse model. For this,
specific estimators, \emph{meta-estimators}, such as the {\tt
GridSearchCV}, take another estimator at construction time, and use
cross-validation internally to set its parameter. When used together with
{\tt cross\_val\_score}, they perform \emph{nested} cross-validation,
\emph{i.e.}~the meta-parameters are set independently of the test data?

@@

\paragraph{A simple text-mining example.}
%
Not every dataset comes as a set of numbers. For instance in natural
language processing (NLP), each observation is a text, \emph{i.e.} a
string, that needs to be transformed into the data matrix expected by
estimators. Typical, features used to build decisions indicate the
presence of certain words, and often their frequencies.
In spam filtering, it can very relevant to extract from a document that
it contains the term \textsf{viagra}, and possibly how many times.
In other NLP problems such as finding proper names,
events such as ``next token is the Roman numeral'' may be relevant, as in
``J.P. Kennedy III''. Counting bigrams, or $n$-grams, can be a way of
capturing this information. Reusing the {\tt transform} API, scikit-learn
provide a few \emph{feature extraction} objects, that can turn such
unstructured data into a data matrix. In these situations, the
$\textbf{X}$ matrix is a
matrix of counting statistics. It is full of zeros, in the sens that very
often a word is present only in a few documents. For better scalability,
it can be encoded using SciPy's sparse matrices, that many scikit-learn
estimators process efficiently.

On Fig.\,\ref{fig:code} we give an example of fully functioning code to
do sentiment polarity classification for movie reviews: given a review,
it outputs whether the review is positive about the movie it concerns.
The code demonstrates the use of pipelines, and also shows how machine
learning ties into unrelated Python's modules: downloading, unpacking and
learning from a dataset are all done in one programming language.

This script first fetches the hand-labeled movie review dataset from
\cite{pang2004} and unpacks it to disk using standard Python libraries.
It then loads these using scikit-learn data loading functions, makes a
pipeline of a \textsf{tf--idf} feature extractor
\cite{rennie2003tackling} --than turns strings into a sparse matrix based
on word frequencies-- and logistic regression, and finally trains the
model. The parameters for the feature extractor and the LogReg classifier
were set manually.

@@

Here, we asked the estimator to predict if the reviews were positive for
a batch of two reviews. The first review is predicted has being not
positive, \emph{i.e.} negative, while the second one is positive. We have
anecdotal evidence that the classifier work. To get a measure for the
classifier's accuracy we retraining it in a cross-validation scheme, this
yield the fraction of correct answers on three different folds:
\begin{lstlisting}
>>> from sklearn import cross_validation
>>> cross_validation.cross_val_score(clf, data.data, data.target)
array([0.9026946, 0.8723724, 0.8633634])
\end{lstlisting}

>>>>

\paragraph{Model evaluation and parameter selection.}
%
The data used to train a model can be used to measure the prediction
error, as it would be enable to distinguish noise from signal, and thus
overly optimistic. The correct way is to leave out \emph{test} data,
untouched during training. Often a \emph{cross-validation} scheme is
used, where the data is repeatedly split into \emph{train} and
\emph{test} subsets. Scikit-learn provides a complete framework for
cross-validation. Specific iterators are used to describe the subsets and
several functions and objects accept as arguments these iterators to
perform cross-validation internally. For instance the {\tt
cross\_val\_score} function measures the prediction score of an
estimator. Cross-validation can also be used to tuned the meta-parameters
of an estimator, such as the sparsity of a sparse model. For this,
specific estimators, \emph{meta-estimators}, such as the {\tt
GridSearchCV}, take another estimator at construction time, and use
cross-validation internally to set its parameter. When used together with
{\tt cross\_val\_score}, they perform \emph{nested} cross-validation,
\emph{i.e.}~the meta-parameters are set independently of the test data.

@@

\paragraph{A simple text-mining example.}
%
Not every dataset comes as a set of numbers. For instance in natural
language processing (NLP), each observation is a text, \emph{i.e.}~a
string, that needs to be transformed into the data matrix expected by
estimators. Typical, features used to build decisions indicate the
presence of certain words, and often their frequencies.
In spam filtering, it can very relevant to extract from a document that
it contains the term \textsf{viagra}, and possibly how many times.
In other NLP problems, such as finding proper names,
events such as ``next token is the Roman numeral'' may be relevant, as in
``J.P. Kennedy III''. A way to capture this information is to count bigrams,
or $n$-grams. Reusing the {\tt transform} API, scikit-learn
provides \emph{feature extraction} objects, that  such
unstructured data into a data matrix. In these situations, the
$\textbf{X}$ matrix is a
matrix of counting statistics. It is full of zeros, in the sens that
often a word is present only in a few documents. For better scalability,
it can be encoded using SciPy's sparse matrices, that many scikit-learn
estimators process efficiently.

On Fig.\,\ref{fig:code} we give an example of fully functioning code to
do sentiment polarity classification for movie reviews: given a review,
it outputs whether the review is positive about the movie it concerns.
The code demonstrates the use of pipelines, and also shows how machine
learning ties into unrelated Python's modules: downloading, unpacking and
learning from a dataset are all done in one programming language.
This script first fetches the hand-labeled movie review dataset from
\cite{pang2004} and unpacks it to disk using standard Python libraries.
It then loads these using scikit-learn data loading functions, makes a
pipeline of a \textsf{tf--idf} feature extractor
\cite{rennie2003tackling} --than turns strings into a sparse matrix based
on word frequencies-- and logistic regression, and finally trains the
model. Parameters for the feature extractor and the LogReg classifier
were set manually.

@@

Here, we asked the estimator to predict if the reviews were positive for
a batch of two reviews. The first review is predicted has being not
positive, \emph{i.e.} negative, while the second one is positive. We have
anecdotal evidence that the classifier work. To get a measure for the
classifier's accuracy we retraining it in a cross-validation scheme, this
yields the fraction of correct answers on three different folds:
\begin{lstlisting}
>>> from sklearn import cross_validation
>>> cross_validation.cross_val_score(clf, data.data, data.target)
array([0.9026946, 0.8723724, 0.8633634])
\end{lstlisting}
